\section{Introduction}
\label{sec:introduction}

In this project, we have investigate non-reciprocal wave propagation in a one-dimensional (1D) beam structure, modulated by a periodic array of piezoelectric patches.

Non-reciprocal structures allow for the transmission of waves in one direction while blocking them in the opposite direction.
This effect is particularly interesting in the context of waveguides and metamaterials, as it can be exploited to design devices such as mechanical dioed and isolators.

\paragraph{Report structure}

Section \ref{sec:theoretical_background} presents the theoretical background needed to understand the problem and the analysis performed.
Numerical methods employed throughout the project are also introduced.

In Section \ref{sec:analysis_shunted_piezo}, the analysis of the shunted piezoelectric patches is performed by means of sensitivity and stability analysis.

In Section \ref{sec:experimental_approach}, the experimental setup is described and the results are presented.
Experimental data are also compared with the numerical results obtained from computational simulations.

Finally, in Section \ref{sec:nonreciprocal_behavior}, the non-reciprocal behavior of the beam structure is highlighted and discussed.

\paragraph{Tools}

For the aim of this work, most of the simulations are carried out using \texttt{MATLAB}.
Additionally, \texttt{Comsol} is also employed to validate the results obtained from \texttt{MATLAB} simulations and experimental data.
